Modeling the Impact of Commodity Prices and Interest Rates on the CAD/USD Exchange Rate: An Analysis of Key Drivers Using Bank Rate and BCPI

### 2024-12-15 paper/paper.qmd
change typo

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-vif1
#| fig-cap: "Variance Inflation Factor (VIF) values for all predictors in the first models are below 5, indicating that multicollinearity is not a concern in these models."
#| layout-ncol: 1
vif_result <- vif(model)
vif_result_df <- data.frame(vif_result)
rownames(vif_result_df) <- c("weekly bank rate", "weekly metal BCPI", "weekly energy BCPI")

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-vif2
#| fig-cap: "Variance Inflation Factor (VIF) values for all predictors in second models are below 5, indicating that multicollinearity is not a concern in these models."
#| layout-ncol: 1
vif_result2 <- vif(model2)
vif_result_df2 <- data.frame(vif_result2)
vif_result_df2 <- round(vif_result_df2, 3)
rownames(vif_result_df2) <- c("weekly bank rate", "weekly total BCPI")
vif_result_df2 %>%
  kbl()
```

>>>>

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-vif1
#| fig-cap: "Variance Inflation Factor (VIF) values for all predictors in the first model are below 5, indicating that multicollinearity is not a concern in these models."
#| layout-ncol: 1
vif_result <- vif(model)
vif_result_df <- data.frame(vif_result)
rownames(vif_result_df) <- c("weekly bank rate", "weekly metal BCPI", "weekly energy BCPI")

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-vif2
#| fig-cap: "Variance Inflation Factor (VIF) values for all predictors in the second model are below 5, indicating that multicollinearity is not a concern in these models."
#| layout-ncol: 1
vif_result2 <- vif(model2)
vif_result_df2 <- data.frame(vif_result2)
vif_result_df2 <- round(vif_result_df2, 3)
rownames(vif_result_df2) <- c("weekly bank rate", "weekly total BCPI")
vif_result_df2 %>%
  kbl()
```
